\documentclass[11pt,letterpaper,roman]{moderncv}
\usepackage[scale=0.8,margin=0.6in]{geometry}
% \usepackage{fontspec} 

% \setmainfont[Ligatures=TeX,
%              Numbers=OldStyle]{IBM Plex Sans}

\moderncvstyle{classic}
\moderncvcolor{blue}

\name{E. Taber}{McFarlin IV}
\title{Software Engineer}
\address{11 Steepletop Rd}{Norwalk, CT 06853}
\phone[mobile]{(203) 644 - 0718}
\email{tabermcfarlin@gmail.com}
% \homepage{tabermcfarlin.com}
\social[linkedin]{taber-mcfarlin}
\social[github]{TaberIV}

\begin{document}

\makecvtitle
\vspace*{-10mm}

\sethintscolumntowidth{mmm yyyy - mmm yyyy}

{
    I have a flexible skill set and I am excited to begin working in software development.
    I have strong programming skills and experience in full stack web development.
    I'm interested in working with modern technologies and learning as much as I can.
    I'm looking for positions in the North East from the New York area to Boston.
}

\section{Education}
\cventry{2015 -- Current}{B.S. Computer Science}{Stevens Institute of Technology}{Hoboken, NJ}{}
{
    \textit{Major GPA -- 3.60, Overall GPA -- 3.49}
    \begin{itemize}
        \item Graduation - May 2019
        \item Member of Upsilon Pi Epsilon, Computing Honor Society
    \end{itemize}
}

\section{Work Experience}
\cventry{August 2018 -- December 2018}{Course Assistant}{\href{http://stevens.edu/}
    {Stevens Institute of Technology}}{Hoboken, NJ}{}
{
    \begin{itemize}
        \item Course Assistant for CS 511, Concurrent Programming. This course covered topics of
              concurrent programming in both Java and Erlang/Elixir.
        \item Provided students with extra help understanding course material and assignments
        \item Graded homework and exams
    \end{itemize}
}
\cventry{May 2018 -- August 2018}{Software Development Intern}
{\href{http://www.arccosgolf.com/}{Arccos Golf}}{Stamford, CT}{}
{
    \begin{itemize}
        \item Designed and implemented a system to make an existing statistical analysis of users'
              golf games easily presentable to those users. (Node.js app)
        \item Solved a probability problem to prevent issues with duplicate product IDs.
              Explored different options to address these issues with CEO.
    \end{itemize}
}
\cventry{2011 -- 2017}{Programming Instructor}{\href{http://www.rowayton.org/}{Rowayton Library}}
{Norwalk, CT}{}
{
    \begin{itemize}
        \item Created and taught a curriculum of basic computer science and game development in
              Scratch for to 8 to 12 year old children.
        \item Tutored both children and adults in learning basic Python programming
    \end{itemize}
}

\section{Projects}
\cventry{September 2018 -- Present}{Engineer Arena}{}{}{}{
    \begin{itemize}
        \item Senior Design project created in a team of 5 with direction from a client
        \item Arena shooter video game created with Unity3D, written in C\#
    \end{itemize}
}
\cventry{Web Development}{\href{http://etmconstruction.com}{ETM Construction Website}}{}{}{}{
    \begin{itemize}
        \item Website for construction business, built with React written in TypeScript.
        \item Hosted at \href{http://etmconstruction.com}{ETMConstruction.com}
    \end{itemize}
}

\section{Skills}
\cvitem{\textbf{Languages}}{JavaScript/TypeScript, C/C++, C\#, Java, Python, Erlang/Elixir}
\cvitem{\textbf{Web Development}}{HTML5, CSS/Sass, React/Redux, MongoDB}
\cvitem{\textbf{Misc. Tech}}{Git, Linux, \LaTeX{}}

\section{Leadership}
\cventry{2017 -- 2019}{President}{\href{stevens.gamedevelopment.club}
    {Stevens Game Development Club}}{Hoboken, NJ}{}
{
    \begin{itemize}
        \item Run weekly club meetings that involve discussion of game design and game programming
              tutorials.
        \item Manage club budget of approximately \$5,000 a year.
        \item Served as treasurer and secretary of the club in 2017 and 2016 respectively.
    \end{itemize}
}


\end{document}
